### 2017-09-29 TF-vldb2018/sec-tsim.tex

\newcommand{\grouprec}{\kw{batch}}
\newcommand{\optgrouprec}{\kw{batch}}
%\newcommand{\grouprecopt}{\kw{kTeamFormOpt}}
\newcommand{\minp}{\kw{minP}}
\newcommand{\rgraphsim}{\kw{undigSim}}
\newcommand{\incsim}{\kw{incSim}}

@@

\revise{
We first propose {\em team simulation}, an extension of traditional graph pattern matching.
We then formally introduce the {\em top-$k$ team formation} problem via team simulation.
We finally present the {\em dynamic top-$k$ team formation} problem.}

@@

\revise{
We first extend pattern graphs of traditional graph pattern matching to carry capacity requirements,
and then define team simulation on undirected graphs.}
%We then redefine strong simulation on directed graphs, originally defined on directed graphs~\cite{MaCFHW14}.}

@@

\vspace{0.5ex}
\ni(2) for each node $u\in V_P$, the number of nodes $v\in V_s$  with $(u, v)\in \Reps$ falls into $f_P(u)$.

@@

\begin{example}
\label{exm-rsimulation}
Consider $P_1$ and $G_1$ in Fig.~\ref{exm-motivation}.
When team simulation with $r=2$ is adopted, $P_1$ matches $G_1$ as there is a perfect subgraph in $G_1$,
\ie the connected component of $G_1$ containing $\kw{PM_{1}}$, which resides in ball
$\ball{[\kw{PM_1}, 2]}$.
It maps \kw{PM}, \kw{BA}, \kw{UD}, \kw{SA}, \kw{SD} and \kw{ST} in $P_1$ to \kw{PM_1}, \kw{BA_1}, \{\kw{UD_1}, \kw{UD_2}\}, \{\kw{SA_1}, \kw{SA_2}\}, \{\kw{SD_1}, \kw{SD_2}\} and \{\kw{ST_1}, \kw{ST_2}\}, respectively.

One can easily verify that
(a) $P_1\eps \ball{[\kw{PM_{1}}, 2]}$, and the ball is exactly the match graph here,
and (b) the capacity bounds on all pattern nodes are satisfied.
\end{example}
\looseness=-1

@@

\revise{
\stitle{Remarks}.
(1) Team simulation differs from graph simulation and strong simulation in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.
%
(2) As for locality constraint, different from strong simulation that requires the matched nodes to locate in a ball with a fixed given radius, team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.

@@

}

>>>>

\newcommand{\grouprec}{\kw{batch}}
\newcommand{\optgrouprec}{\kw{batch}}
%\newcommand{\grouprecopt}{\kw{kTeamFormOpt}}
\newcommand{\minp}{\kw{minP}}
\newcommand{\rgraphsim}{\kw{undirgSim}}
\newcommand{\incsim}{\kw{incSim}}

@@

We first propose {\em team simulation}, a revision of traditional graph pattern matching.
We then formally introduce the {\em top-$k$ team formation} problem via team simulation.
We finally present the {\em dynamic top-$k$ team formation} problem.

@@

We first extend pattern graphs of traditional graph pattern matching to carry capacity requirements,
and then define team simulation on undirected graphs.
%We then redefine strong simulation on directed graphs, originally defined on directed graphs~\cite{MaCFHW14}.}

@@

\vspace{0.5ex}
\ni(2) for each node $u$ in $P$, the number of nodes $v$ in $G_s$  with $(u, v)\in \Reps$ falls into $f_P(u)$.

@@

\begin{example}
\label{exm-rsimulation}
Consider pattern $P_1$ and data graph $G_1$ in Fig.~\ref{exm-motivation}, and  team simulation with $r=2$ is adopted.

One can easily verify that $P_1$ matches $G_1$  via team simulation, \ie $P_1 \eeps G_1$, 
as (a) there is a perfect subgraph in in ball
$\ball{[\kw{PM_1}, 2]}$, \ie the connected component of $G_1$ containing $\kw{PM_{1}}$, which maps \kw{PM}, \kw{BA}, \kw{UD}, \kw{SA}, \kw{SD} and \kw{ST} in $P_1$ to \kw{PM_1}, \kw{BA_1}, \{\kw{UD_1}, \kw{UD_2}\}, \{\kw{SA_1}, \kw{SA_2}\}, \{\kw{SD_1}, \kw{SD_2}\} and \{\kw{ST_1}, \kw{ST_2}\}, respectively, and, moreover, (b) the capacity bounds on all pattern nodes are satisfied.
\end{example}

@@

\stitle{Remarks}.
(1) Team simulation differs from graph simulation~\cite{infsimu95} and strong simulation~\cite{MaCFHW14} in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.

\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.

@@
